Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-10-21 demystify.tex
updates

Ultimately, this is a personal choice and you do what you feel comfortable.
If you do not feel comfortable disclosing this, you should not feel pressured to do so.
However, if you feel comfortable but are unsure if it is accepted in higher education in the US, then I hope this section helps you understand that it is not only accepted but also valued and appreciated.

>>>>

Ultimately, this is a personal choice and you do what you feel comfortable.
If you do not feel comfortable disclosing this, you should not feel pressured to do so.
However, if you feel comfortable but are unsure if it is accepted in higher education in the US, then I hope this helps you understand that it is not only accepted but also valued and appreciated.
